Runtime Feedback in a Meta-Tracing JIT for Efficient Dynamic Languages

### 2011-04-14 talk/icooolps2011/paper.tex
enable preprint option
will ignore this XXX
this is repetition

\cfbolz{XXX more precise definition of what promote does}

@@

The PyPy JIT generator automatically detects the majority of these conditions.
However, for the cases in which the automatic detection does not work, the
interpreter author can apply \textbf{hints} to improve the optimization
opportunities. There is one kind of hint for both of the conditions above.

>>>>

@@

There is one kind of hint for both of these conditions.
